---
title: "Premier League Untitled"
author: "Ansel Alldredge"
date: '2023-04-20'
output:
  pdf_document:
    fig_height: 5
    fig_width: 6.5
  word_document: default
  html_document:
    df_print: paged
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE, message=FALSE}
library(tidyverse)
library(rvest)
```


# load epl matches csv
```{r}
epl_matches_data <- read_csv("./data/eplmatches.csv")
```
# function mchwk_tbl_fillna
```{r}
tbl_fill_na <- function(df) {
  nrows <- nrow(df)
  nmore <- 22 - nrows
  
  # add nmore more rows
  for(i in 1:nmore) {
    df[nrows + 1,] <- NA
    nrows <- nrows +1
  }
  return (df)
}
```



# function create_matchweek_table() returns a table for the end of a single matchweek for a single year
```{r}
create_matchweek_table <- function(endyear, week) {
  url <- paste("https://www.worldfootball.net/schedule/eng-premier-league-", endyear - 1, "-", endyear, "-spieltag/", week, "/", sep="")
  
  # return if path not allowed
  if(!robotstxt::paths_allowed(url)) return(-1)
  
  year_vec <- rep(endyear, 20)
  week_vec <- rep(week, 20)
  
  parsed_html <- read_html(url)
  
  position <- parsed_html %>%
    html_nodes(":nth-child(7) .standard_tabelle td:nth-child(1)") %>%
      html_text()
  
  team <- parsed_html %>%
    html_nodes(":nth-child(7) .standard_tabelle a") %>%
      html_text()
    
  played <- parsed_html %>%
    html_nodes(":nth-child(7) .standard_tabelle td:nth-child(4)") %>%
      html_text()
    
  wins <- parsed_html %>%
    html_nodes(":nth-child(7) .standard_tabelle td:nth-child(5)") %>%
      html_text()
    
  draws <- parsed_html %>%
    html_nodes(":nth-child(7) .standard_tabelle td:nth-child(6)") %>%
      html_text()
    
  losses <- parsed_html %>%
    html_nodes(":nth-child(7) .standard_tabelle td:nth-child(7)") %>%
      html_text()
    
  goals_for_against <- parsed_html %>%
    html_nodes(":nth-child(7) .standard_tabelle td:nth-child(8)") %>%
      html_text()
    
  goal_diff <- parsed_html %>%
    html_nodes(":nth-child(7) .standard_tabelle td:nth-child(9)") %>%
      html_text()
    
  points <- parsed_html %>%
    html_nodes(":nth-child(7) .standard_tabelle td:nth-child(10)") %>%
      html_text()
  
  table <- tibble(
      year = year_vec,
      week = week_vec,
      position = position,
      team = team,
      played = played,
      wins = wins,
      draws = draws,
      losses = losses,
      goals_for_against = goals_for_against,
      goal_diff = goal_diff,
      points = points
    )
  
  #table <- tbl_fill_na(table)
  
  return(table)
}

```

# function make_year(year, max_weeks) returns a dataframe with all tables from the end of all matchweeks for a single year
```{r}
create_year_table <- function(year, max_weeks) {
  year_table <- create_matchweek_table(year, 1)
  for (i in 2:max_weeks) {
    week_table <- create_matchweek_table(year, i)
    year_table <- rbind(year_table, week_table)
  }
  return(year_table)
}
```

# create full year for 2022
```{r}
table_2022 <- create_matchweek_table(2022, 1)
for (i in 2:38) {
  week_table <- create_matchweek_table(2022, i)
  table_2022 <- rbind(table_2022, week_table)
  
}
```

# function make_year_range(year_range) makes a dataframe with all tables from the end of all matchweeks for a range of years
```{r}
make_year_range <- function(year_range) {
  
}
```

